---
title: "Florencia D'Andrea's CV"
author: Florencia D'Andrea
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "./data/",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at _ https://flor14.github.io/cvitae_datadriven/cv.html_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/flor14/cvitae_datadriven/raw/master/cv_english.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```



<!-- Language Skills {#skills} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- CV %>% print_skill_bars() -->
<!-- ``` -->



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown). 

The source code is available [on github.com/nstrayer/cv](https://github.com/flor14/cvitae_datadriven.git).

Last updated on `r Sys.Date()`.



Main
================================================================================

Florencia D'Andrea {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```



Formación Académica {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```



Experiencia en Investigación {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_positions')
```


Publicaciones Científicas en Revistas Internacionales  {data-icon=chart-line}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('data_science_writing_aside')
```
:::

```{r}
CV %<>% print_section('data_science_writing')
```

Publicaciones en Congresos (selección)   {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('congresos')
```

Cursos y Certificaciones {data-icon=suitcase}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('cursos')
```
:::

```{r}
CV %<>% print_section('cursos')
```

Experiencia en Docencia {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------


```{r}
CV %<>% print_section('teaching_positions')
```


Formación de Recursos Humanos {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('rrhh')
```

Charlas  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('charlas')
```


Organización de Eventos de CyT {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('eventos_cyt')
```

Comunidades  {data-icon=laptop}
--------------------------------------------------------------------------------
::: aside
```{r}
CV %<>% print_text_block('teaching_experience_aside')
```
:::

```{r}
CV %<>% print_section('comunidades')
```


Extensión {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('extension')
```


Otros Antecedentes {data-icon=chart-line}
--------------------------------------------------------------------------------
::: aside
```{r}
CV %<>% print_text_block('otros')
```
:::
```{r}
CV %<>% print_section('otros')
```


```{r}
CV %<>% print_links()
```

